---
title             : "Writing an academic paper using papaja and RStudio: A moderated mediation diary study"
shorttitle        : "writing with papaja"

author: 
  - name          : "Henrik Sørlie"
    affiliation   : "1,2,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Artikkelgata 1, 0001 Oslo"
    email         : "henrik.sorlie@uib.no"
  - name          : "Mads Medforfatter"
    affiliation   : "2,3"
  - name          : "Pernille Psykolog"
    affiliation   : "1,3"

affiliation:
  - id            : "1"
    institution   : "Norwegian Defence Command and Staff College, Norwegian Defence University College"
  - id            : "2"
    institution   : "Department of Psychosocial Science, University of Bergen"
  - id            : "3"
    institution   : "Institutt for kvasipsykologi, Livets Harde Høgskole"

authornote: |

  The authors declare no conflict of interest.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "motivation, cognition, zombies, pancakes"
wordcount         : "1356"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(psych)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(47)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Life is hard.
And so is writing the introduction to a paper.
Here I have quoted some sources [@alfesTestingAdditiveInteractive2016; @barrickSelectionFit2019a].
And here I have quoted even more [@gurbuzPossibleAntecedentsMilitary2009a; @koopmanWhyWhomDoes2019; @robisonPupillometryTracksFluctuations2018].
It should be clear by now that this is a really good paper.
Thus, we hypothesize:

H1: This is an awesome paper.

# I like pancakes

Pancakes are good [@deciSelfDeterminationTheoryWork2017; @demeroutiProductiveCounterproductiveJob2015].
I could eat pancakes all day.

H2: This hypothesis is better than the last one.

# Methods

```{r data}
data <- tibble(
  gender = factor(as.character(rbinom(100, 1, 0.4)), levels = c("0", "1"), labels = c("female", "male")),
  age = rpois(100, 23),
  motivation = rnorm(100),
  pancakeliking = rnorm(100),
  zombieness = 0.3 * pancakeliking + 0.2 * motivation + 0.5 * rnorm(100)
)
```

```{r}
glrstab<- function(x, export=FALSE) {
 
 r <-corr.test(x)$r	#taking just the correlation matrix; no N, or p
 p <-corr.test(x)$p	#taking the p*s
 
#define notions for significance levels
 mystars <- ifelse(p < .001, "**"
                   , ifelse(p < .01, "**"
                            , ifelse(p < .05, "*"
                                     , ifelse(p < .10, "+", " "))))
 
 #round r, define new matrix Rnew with the correlations from rnd and paste mystars
 rnd  <- papaja::printnum(r, gt1 = FALSE, digits = 2)  #round, drop leading 0 - Thanks CRSH!								                     
 Rnew <- matrix(paste(rnd, mystars, sep=""), ncol=ncol(rnd)) 
 
  #remove 1.0 correlations from diagonal  and set the strings
 diag(Rnew) <- ''		
 Rnew[upper.tri(Rnew)] <- ''								                	
 
 rownames(Rnew) <- paste(1:ncol(rnd), colnames(rnd), sep=" ")         #define number and name
 colnames(Rnew) <- paste(1:ncol(rnd), "", sep="") 			       #define number
 
#fun-part: we trim the top half 
 Rnew[upper.tri(Rnew)] <- ''			
 Rnew
 
 Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		     #describe x, M sD - put them in the matrix
 colnames(Rnew)[1:2] <- c("M","SD")					      		#Beschriftung der neuen Spalten
 Rnew <- Rnew[,1:(ncol(Rnew)-1)]							        	#delete the last column (ugly)
 
 #export to clipboard
 
   if (export==TRUE){
   result<-write.table(Rnew
                       , "clipboard"
                       , sep=";"
                       , row.names=FALSE)
 }
 else result <- Rnew
 return(result)
 
}
```


## Participants
Our sample consisted of `r printnum(length(data$gender))` first-year psychology students, of which `r printnum(nrow(filter(data, gender == "female")), numerals = FALSE, capitalize = FALSE)` were female and `r printnum(nrow(filter(data, gender == "male")), numerals = FALSE, capitalize = FALSE)` were male.
The mean age was `r printnum(mean(data$age))` years ($SD = `r printnum(sd(data$age))`$).

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results
```{r descriptivestable, message=FALSE, warning=FALSE, results="asis"}

descriptives <- glrstab(data[-1]) #Correlation matrix

rownames(descriptives) <- c("1 - Age", "2 - Motivation", "3 - Pancake liking", "4 - Zombieness")
colnames(descriptives) <- c("$M$", "$SD$", "1", "2", "3")

apa_table(descriptives, escape  = FALSE, caption = "Descriptive statistics of study variables", note = "* p < .05, ** p < .01, *** p < .001", landscape = FALSE)

```
Table \@ref(tab:descriptivestable) shows the means, standard deviations and correlations between all study variables. A significant correlation was found between pancakeliking and zombieness (`r `). 

# Discussion
```{r firstplot, fig.cap="This plot says it all", fig.align="center"}
plot1 <- ggplot(data, mapping = aes(pancakeliking, zombieness))+
  geom_point()
plot1
```
Without a doubt, there is a lot to discuss.
As shown in figure\ \@ref(fig:firstplot), our findings indicate several things.

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
